---
title: "Lab 07 - University of Edinburgh Art Collection"
author: "Insert your name here"
date: "Insert date here"
output: github_document
---

### Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse) 
library(skimr)
```

```{r load-data, message = FALSE, eval = TRUE}
# Remove eval = FALSE or set it to TRUE once data is ready to be loaded
uoe_art <- read_csv("data/uoe-art.csv")
```

### Exercise 10

```{r separate-title-date, error = TRUE}
uoe_art <- uoe_art %>%
  separate(title, into = c("title", "date"), sep = "\\(") %>%
  mutate(year = str_remove(date, "\\)") %>% as.numeric()) %>%
  select(title, artist, year, link)
```
The warning is fine because it's just saying it's filling in the missing dates with NA. 

### Exercise 11

```{r data_skim}
skim(uoe_art)
```
1 has a missing title, 115 have missing artists, 0 have missing links, and 1369 have missing years.


### Exercise 12

```{r year_hist}
ggplot(data = uoe_art, aes(x = year)) +
  geom_histogram(binwidth = 1)
```

I just did table(uoe_art$year) and found that there's a datapoint at year 2, which is what is messing with this graph. Let's look at it.

```{r look_2}
uoe_art %>% 
  filter(year == 2)

```
Okay, so it's called Death Mask(2) and that's where the confusion is. Let's change it to the real year and name.

##Exercise 13

```{r mut_2}
uoe_art$year[uoe_art$year == 2] <- 1964
uoe_art$title[uoe_art$title == "Death Mask"] <- "Death Mask(2)"
```

Just checked with table and it's correct. Now we'll redo the histogram.

```{r year_hist_2}
ggplot(data = uoe_art, aes(x = year)) +
  geom_histogram(binwidth = 2) +
  labs(x = "Year", y = "Count", title = "Count of art by year")
```
## Exercise 14

```{r ar}
uoe_art %>%
  count(artist) %>%
  arrange(desc(n))
```

Besides the prominent "Unknown," Emma Gillies is byfar the most featured artist. My guess for why this museum has so much of her work is that she's from Edinburgh.  

